\chapter*{Abstract}
As per requirement of the Computational Creativity course, a creative system will be designed and constructed.
This will be done by completing multiple smaller milestones.
This report focuses on the fourth of those milestones.
Some more information is given about both the internal validation strategy of the GAN as well as the external validation that will be done to assess the quality and creativity of the system.
A PHP survey tool has been made that allows for easy online and offline external validation of the system.
A lot of progress on the implementation of the GAN and control over it has also been made.

%TODO
Part \ref{part:progress_on_gan} discusses the progress made on the implementation and control over the GAN. 
Since it might be the first time for the peer-reviewers to hear of this project a short revision of what this project is about is given in section \ref{sec:short_reminder}. 
Further sections of this part defend the choice for a pre-trained GAN and the extensions made to the GANSpace tool.

Part \ref{part:evaluation} discusses the evaluation that will be done for this project.
In section \ref{sec:internal_validation} the internal validation that is fundamental to GANs is discussed.
External validation and the PHP tool created for it is discussed later in the part as well as some further remarks on the evaluation strategy.

All source files for this project are available on GitHub \citep{github_project}. It is noted that this report is written by modifying the VUB based \LaTeX{} template from \citet{latex_template}. 